Optimal Duplicate Detection in a Sliding Window

### 2020-03-27 qhtv2.tex
Abstract

\title{Adapting Duplicate Filters to a Sliding Window Context}

@@

%% Abstract
\begin{abstract}
	A duplicate detection filter is an online data structure designed to efficiently detect repetitions (duplicates) in a stream, when only a limited amount of memory is available. A well-known data structure used in this context is the Bloom filter, which has been generalised in several ways to 
	improve its performances or strike specific tradeoffs.

	When analysed in the limit of an infinite stream, error rates of duplicate filters turn out to be heavily constrained; as a consequence they appear to provide no advantage, asymptotically, over a random biased coin toss \cite{10.1145/3297280.3297335}.

	In this paper we consider a \enquote{windowed} variation on the duplicate detection problem
	that is better-behaved and thus lends itself to a more thorough 
	mathematical analysis. We show how existing filters can be adjusted to work
	in this new setting using a queuing construction. 
\end{abstract}

>>>>

\title{Optimal Duplicate Detection in a Sliding Window}

@@

%% Abstract
\begin{abstract}
	Duplicate detection is the problem of identifying whether a given item has previously appeared in a (possibly infinite) stream of data, when only a limited amount of memory is available.

	Building on the Bloom filter \cite{bloom_spacetime_1970}, an early data structure amenable to duplicate detection, several generalisations and variants were proposed tthat reduce error rates while maintaining constant memory.

	Unfortunately the infinite stream setting is ill-posed, and error rates of duplicate detection filters turn out to be heavily constrained: as a consequence they appear to provide no advantage, asymptotically, over a random biased coin toss \cite{10.1145/3297280.3297335}.

	Both as a better-behaved setting and as a construction technique, a
	\emph{windowed} variant of the duplicate detection problem was 
	introduced in \cite{She08,Yoo10}, which consists in finding duplicate 
	entries amongst the last $w$ elements of the stream for a fixed integer $w$.

	In this paper we formalise this setting, and show that a perfect (zero error) solution can be used up to a maximal window size $w_\text{max}$. Above this threshold we show that some existing duplicate detection filters (designed for the \emph{non-windowed} setting) perform better that those targeting the windowed problem. Finally, we introduced a \enquote{queuing construction} that improves on the performance of some duplicate detection filters in the windowed setting. 
\end{abstract}
